Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-09 paper.tex
Updates in method

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected for every subject is randomly selected in
a triangular distribution with parameters \textit{a}, \textit{b} and 
\textit{c} (\todo{see Figure X}) where \textit{b} is set to $N_{f}$ and the other two 
parameters can be set with two approaches meant to ensure that the 
average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
ratio):
\begin{enumerate}
        \item Largest-a (RFNT-L): In this approach, a is set to the 
        largest possible value, i.e., b. The average of the 
        distribution is $\frac{a+N_{f}}{2}$, therefore, 
        a=$(2\alpha-1)N_{f}$.
\end{enumerate}

By considering $\alpha$ 
as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
for $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would 
get a negative value in this regard, therefore to avoid this issue the uniform distribution 
is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following 
approaches are applicable. This distribution aims at sampling files produced towards 
the end of the pipeline execution.

Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a (RFNT-L):  
This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the two other 
parameters are reperesent the limmited bond and mode of the distribution respectively. 
The \textit{\textbf{a}} equals to $\nicefrac {N_{f}(3\alpha-1)}{2}$ while \textit{\textbf{c}} 
is considered as equal as \textit{\textbf{a}}, $(\textit{\textbf{c}} = \textit{\textbf{a}})$.\\

In this approach there is a concern to eliminate the possibility of having less 
than the first two generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.

\item Smallest-a (RFNT-S):
This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the
two other parameters are reperesent the limmited bond and mode of the distribution respectively. 
The \textit{\textbf{a}} is set to $0$  while \textit{\textbf{c}} equals to $N_{f}(3\alpha-1)$.\\
In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
that some subjects be reperesented in the training set just by their first generated file and no more files.

\end{enumerate}

>>>>

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected for every subject is randomly selected in
a triangular distribution with parameters \textit{a}, \textit{b} and 
\textit{c} (\todo{see Figure X}). The mean of the distribution is 
$\frac{a+b+c}{3}$. In our case, we set \textit{c} to $N_{f}$ and we set 
\textit{a} and \textit{b} with two approaches meant to ensure that the 
average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
ratio):
\begin{enumerate}
        \item Largest a (RFNT-L): a is set to the 
        largest possible value, i.e., b. The average of the 
        distribution is $\frac{2a+N_{f}}{3}$, therefore 
        $a=\frac{3\alpha-1}{2}N_{f}$.
                \item Smallest a (RFNT-S): a is 
        set to the smallest possible value, i.e., 0. The average of the 
        distribution is $\frac{b+N_{f}}{3}$, therefore 
        $b=N_{f}(3\alpha-1)$. To ensure that $b<N_{f}$, we actually set 
        $b=\min(N_{f}, N_{f}(3\alpha-1))$. 
\end{enumerate}
It should be noted that $\alpha$ must be larger than $\frac{1}{3}$ for 
a and b to remain positive. For training ratios lower than $\frac{1}{3}$, we 
define RFNT methods as the RFNU one presented previously.

As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
and~\ref{fig:triangular-S-Sample-Training-set}, the motivation for the 
RFNT-L method is to guarantee that, for large enough values of 
$\alpha$, all subjects will have at least a few files in the training 
set.
